2 Party State Channels with State Assertions

### 2019-01-14 paper/main.tex
Updated typos in paper pseudocode
Small updates and added sections for n-party and for implementation

	\title{2 Party State Assertion Channels }

@@

Cryptocurrencies do not scale.
The community are pursing three approaches to alleviate the scalability issue which includes new blockchain protocols \cite{bano2017consensus}, sharding transactions into distinct processing areas and off-chain protocols. 
While the first two approaches can strictly increase the network's throughput, they harm the network's public verifiability as it reduces  the diversity of peers with the computatonal, bandwidth or storage requirements to validate all transactions on the network and ultimately hold the miner's accountable. 
This paper focuses on the off-chain (or so-called Layer 2) approach that simply aims to reduce the network's load.
One promiment off-chain approach are state channels that lets a group of parties process transactions (and execute a smart contract) locally amongst themselves instead of the global network. 
In the best case, the application is no longer restricted by the underlying blockchain's latency and all execution is free as it remains local between the parties. 
If there is a disagreement about the latest state of the smart contact, then any party can trigger a dispute and rely on the underlying blockchain to arbitrate the dispute's outcome.
To arbitrate, the blockchain provides a fixed time period to collect evidence from all online parties before using this evidence to decide the off-chain smart contract's new state. 
So far, there are two types of dispute processes for a state channel. 
The first is a \emph{closure dispute} \cite{statechannelnetworks,battleship,celernetwork} as the dispute process is responsible for closing the channel, re-deploying the smart contract with the new state and letting parties continue its execution via the blockchain. 
The second is a \emph{command-issuance dispute} \cite{miller2017sprites,mccorry2018pisa,counterfactual} as the dispute process collects commands from each party and then executes the command to compute the new state. 
A recent case study empirically evaluated state channels as a scaling solution by building the  two player game battleship \cite{battleship}.
They highlighted the most expensive aspect of any dispute process is sending the application's full state. 
For example, the  case study claimed that sending the full game state approximately costs \$1.57 when the blockchain is not congested, but it can potentially sky-rocket to \$57.57 if the blockchain is congested. 
The above can clearly hamper real-world use of state channels as an honest party will not use the dispute process if it is too clostly (and thus they cannot self-enforce the application's correct execution). 
We propose, \emph{State Assertion Channels}, which has a command-issuance dispute process\footnote{The assertion concept isn't compatible with closure channels as the full state is required to re-deploy an application.}.  and overcomes the issue of sending the application's full state by leveraging the concept of an optimistic contract.
Our contributions:

\begin{itemize}
	\item We propose the first state channel that ensures an honest party never pays the cost to send the applicaton's full state during the dispute proess.  
	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 
\end{itemize}

@@

An optimistic smart contract trades the cost of computation with time.
This lets a smart contract accept an application's new state if no one has proved it is invalid within a fixed challenge period. 
Briefly, one party submits the application's $\stateinfoi$, a command $\cmd$, its $\inputs$, the next $\stateinfoplus$ and a financial bond. 
Thi asserts that $\stateinfoplus$ is the next state if the smart contract were to compute  $\stateinfoplus = \texttt{Transition}(\stateinfoi, \cmd, \inputs)$. 
Other interested parties can compute the transition locally to verify its validity.
If the asserted state is invalid, then anyone can issue a challenge by notifying the smart contract to compute the transition.
If the challenge is successful, then the bond is used to refund the challenger. 
Eigenmann, Moore and Johnson provided the first implementation of an optimistic contract for the Ethereum Name Service
\cite{optimisticcontracts}, but so far this technique has alluded real-world use.

\paragraph{Command Issuance State Channels}
Sprites proposed the concept of a command-issuance state channel, and since then it has been extended by PISA \cite{mccorry2018pisa}, Counterfactual \cite{coleman2018counterfactual} and Magmo \cite{magmo}. 
At a high level, one party can submit the latest $\stateinfoi$ agreed by all parties before triggering the dispute process.
The smart contract provides a fixed time period for all parties to submit commands and the contract is responsible for computing every command (i.e. state transition).
In Sprites (and PISA), all commands are executed after the dispute process has expired.
Whereas in Counterfactual and Magmo, the command is executed when it is submited and the dispute period's expiry time is reset (i.e. it dispute period is extended for every command). 
The dispute process can be cancelled if one party submits a later state agreed by all parties, or after the expiry time.

\section{State Assertion Channels}
We provide a high level overview of state assertion channels to show how it combines optimistic contracts and command issuance channels.
Afterwards we'll provide a list of assumptions for the application contract $\appblue$ to ensure new assertions can always be challenged. 
Finally we'll present the state assertion channel contract $\chanblue$ and the interaction amongst both parties, $\chanblue$ and $\appblue$.

@@

The state assertion contract $\chanblue$ and the application contract $\appblue$ must be deployed on the blockchain.
Each party must lock coins into the state channel before they can begin co-operatively executing the application off-chain amongst themselves. 
If there is a disagreement off-chain, then both parties can continue its progression via the dispute process.
Our contribution involves changing the dispute process to avoid sending the full application's state.
Instead parties will assert an application's new state by submitting a hash of the previous state $\hstatei$, the command $\cmd$, its $\inputs$, a hash of the next state $\hstateplus$ and a financial \texttt{bond}. 
%This asserts that $\hstateplus$ represents the application's new state if the command (and its input) was executed by $\appblue$. 
The dispute process provides a fixed time period for the counterparty to verify the assertion by computing the state transition locally. 
To challenge an assertion, the party submits the previous $\stateinfominus$ which lets $\chanblue$ verify the assertion was indeed correct by executing the transition via $\appblue$.  
If the honest party successfully challenges an assertion and proves it is invalid, then they are sent the \texttt{bond} as a refund.
Thus an honest party can always continue an applicaton's execution by asserting a hash of the next state, and they are always refunded the cost of challenging an invalid assertion.

@@

\paragraph{Turn-based application} 
We assume it is a turn-based application and each party performs their state transition in turn. 
As well, $\appblue$ must be instantiated on the blockchain to ensure its address is provided to the  state assertion contract $\chanblue$.

@@

\paragraph{Channel status} 
The channel has three flags $\texttt{Status} = \{\DEPOSIT, \ON, \DISPUTE\}$. 
Both parties must deposit coins in $\chanblue$ before it will transition from $\DEPOSIT \rightarrow \ON$.  
While the channel's status is set as $\ON$ both parties can co-operatively continue the application's progression off-chain by exchanging signatures for new states.
If there is a disagreement about a state transition, then one party can trigger a dispute which changes the status from $\ON \rightarrow \DISPUTE$. 
The contract self-enforces a turn-based dispute process.
One party asserts a new state, and the other party can either challenge it by notifying the contract to check the state transition, or they can approve it by asserting a new state which extends it. 
The dispute process can only finish and let the status change from $\DISPUTE \rightarrow \ON$ if one party submits a co-operatively signed new state.

@@

\paragraph{Proof of concept implementation} 
Our proof on concept implementation took 2,943,664 gas to deploy. Which  is approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127, the real world rate in January 2019. The cost to make a state assertion is 59,774+39.5n gas (\$0.02), where \textit{n} corresponds to the number of bytes supplied as $\inputs$ to the assertion.

@@

\paragraph{Enforcing time-based events} 
The assertion channel is responsible for enforcing time-based events with the dispute period $\Delta$ and the application doesn't need to consider it. 
When the application is co-operatively progressing off-chain, an honest party will wait for a local timeout before triggering a dispute via the blockchain. 
For every new state assertion, the dispute process is reset to ensure each party has a time period of $\Delta$ to take their next move. 
If a party doesn't assert a new state before the deadline, then the honest party will notify the contract via $\chanblue.\timeoutblue()$.
This terminates the application and sends all coins (including the bonds) to the honest party.

@@

\paragraph{Offline parties and PISA} 
There are two issues for a watching service like PISA \cite{mccorry2018pisa} to protect the channel. 
First, an attacker can trigger a dispute with the latest agreed state hash, and then assert an invaid state hash that benefits the attacker.
A watching service must have a copy of the latest state in plaintext to verify the invalid state transition and issue a challenge, but this hinders state privacy.
Second, an attacker can issue a new state assertion and claim all coins after the deadline using $\chanblue.\timeoutblue()$. 
To prevent a timeout, the offline party must delegate the authority to continue the application's execution to the watching service.
Future work should consider whether the execution of an application can be delegated to a third party in an accountable manner.

@@

\begin{figure}[H]
	\begin{boxedminipage}{\columnwidth}
		\begin{tabular}{l}
			\contract StateAssertionChannel \{ \\
			\quad $\enum$ Status \{$\DEPOSIT$, $\ON$, $\DISPUTE$\}, $\addr$[] plist; \\
			\quad Status status; $\uintno$ deadline; $\hashblue$ $\hstatei$, $\uintno$ i; $\addr$ turn; \\ %\comment{// Latest state info}  \\
			\quad $\addr$ asserter; $\hashblue$ $\hstateplus$; $\bytes$ input; $\uintno$ cmd; $\bool$ assertion; \\
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ setstate($\bytes[]$ \_sigs, $\uintno$ \_i, $\addr$ \_turn, $\hashblue$ \_$\hstatei$) \{ \\
			\quad \quad \require(\_i $>$ i)); \comment{ // Largest counter so far} \\
			\quad \quad $\hashblue$ hmsg = hash(\_i, \_$\hstatei$,\_turn, $\addr(\this)$);  \\
			\quad \quad \require(verifySigs(hmsg, sigs, plist));  \comment{// Everyone signed new hstate} \\
			\quad \quad delete(input,cmd,\hstateplus,asserter, assertion); \comment{// Delete assertion}\\
			\quad \quad status = Status.\ON; i = \_i; $\hstatei$ = \_$\hstatei$;  turn = \_turn; \comment{// Agreed state} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ triggerDispute() \{ \\
			\quad \quad $\require$(status == Status.ON \& onlyParties()); \comment{// Only parties trigger} \\
			\quad \quad  status = Status.DISPUTE; deadline = now + disputePeriod;\\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ assertState($\hashblue$ \_$\hstatei$, $\hashblue$ \_$\hstateplus$, $\bytes$ \_input, $\uintno$ \_cmd) \{ \\
			\quad \quad $\require$(status == Status.DISPUTE \texttt{AND} checkCallerTurn()); \\
			\quad \quad $\ifs($!assertion)  \{ \\ 
			\quad \quad \quad assertion = true; $\require(\hstatei == \_\hstatei)$ \comment{// First assertion}  \\ 
			\quad \quad \} $\elses$ \{ $\require$($\hstateplus$ == \_$\hstatei$); \} \comment{// Extending existing assertion} \\ 
			\quad \quad asserter = $\msgsender$; input = \_input; cmd = \_cmd; \comment{// Store assertion} \\
			\quad \quad $\hstatei$ = $\hstateplus$; $\hstateplus$ = \_$\hstateplus$; \comment{// i accepted. i+1 assertion} \\ 
			\quad \quad deadline = now + disputePeriod; \comment{// Reset deadline after an assertion} \\
			\quad \}

		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ challengeAssertion($\bytes$ \_oldstate) \{ \\
			\quad \quad \require(status == Status.DISPUTE); \require(asserter != $\msgsender$);  \\
			\quad \quad \require($\hstatei$ == hash(\_oldstate) AND assertion); \comment{// Assertion exists} \\
			\quad \quad $\hashblue$ checkh = $\appblue.\transitionblue$(asserter, \_oldstate, input, cmd); \comment{// Compute} \\ 
			\quad \quad $\ifs$($\hstateplus$ != checkh) \{ \comment{// Send all coins and bond to non-cheater.}  \} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ timeOut() \{ \\
			\quad \quad \require(now $>=$ deadline \&\& status == Status.dispute); \\ 
			\quad \quad \comment{// Send all coins/bonds to asserter (i.e. last party to respond).} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ resolve($\uintno$ balance1, $\uintno$ balance2) \{ \\
			\quad \quad $\ifs$(status == Status.Dispute) \{ \\
			\quad \quad \quad $\require$(checkCallerTurn()); \comment{// Non-asserter must resolve b4 timeout.} \\
			\quad \quad \} $\elses$ \{ \require(status == Status.ON); \} \comment{// No on-going dispute.} \\ 
			\quad \quad $\require$(hstate == hash(balance1, balance2)); \comment{// Terminal state?} \\
			\quad \quad \comment{// Send each party their final balance and bond.} \\
			\quad \}
		\end{tabular}

	   	\begin{tabular}{l}
	   		\quad $\oninput$ deposit(); \comment{// Not implemented due to space - INCLUDES BOND} \\
	   		\quad $\oninput$ onlyParties() $\returns(\bool)$; \comment{// Check if tx signer is whitelisted} \\
	   		\quad $\oninput$ refundAllBonds() $\internal$; \comment{// Refunds all bonds} \\
	   		\quad $\oninput$ checkCallerTurn() $\returns$($\bool$); \comment{Enforce turn based disputes} \\
	   		\quad $\oninput$ verifySigs($\bytes$ hmsg, $\bytes[]$ sigs, $\addr[]$ signers) $\returns(\bool)$; \\
	   		\}
	   \end{tabular}
	\end{boxedminipage}

>>>>

	\title{2 Party State Channels with State Assertions }

@@

Cryptocurrencies do not scale.
The community is pursing three approaches to alleviate the scalability issue. These are: new blockchain protocols \cite{bano2017consensus}, sharding transactions into distinct processing areas and off-chain protocols. 
While the first two approaches can strictly increase the network's throughput, they harm the network's public verifiability as they reduce the diversity of peers with the computatonal, bandwidth or storage requirements to validate all transactions on the network and ultimately hold the miner's accountable. 
This paper focuses on the off-chain (or so-called Layer 2) approach that simply aims to reduce the network's load.
One promiment off-chain approach are state channels that lets a group of parties process transactions (and execute a smart contract) locally amongst themselves instead of on the global network. 
In the best case, the application is no longer restricted by the underlying blockchain's latency and all execution is free as it remains local between the parties. 
If there is a disagreement about the latest state of the smart contact, then any party can trigger a dispute and rely on the underlying blockchain to arbitrate the dispute's outcome.
To arbitrate, the blockchain provides a fixed time period to collect evidence from all online parties before using this evidence to decide the off-chain smart contract's new state. 
So far, there are two types of dispute processes for a state channel. 
The first is called \emph{closure dispute} \cite{statechannelnetworks,battleship,celernetwork} as the dispute process is responsible for closing the channel, re-deploying the smart contract with the new state and letting parties continue its execution via the blockchain. 
The second is called \emph{command-issuance dispute} \cite{miller2017sprites,mccorry2018pisa,counterfactual,magmo} as the dispute process collects commands from each party and then executes the command to compute the new state. 
A recent case study empirically evaluated state channels as a scaling solution by building the  two player game battleship \cite{battleship}.
They highlighted the most expensive aspect of any dispute process is sending the application's full state. 
For example, the  case study claimed that sending the full game state approximately costs \$1.57 when the blockchain is not congested, but it can potentially sky-rocket to \$57.57 if the blockchain is congested. 
The above can clearly hamper real-world use of state channels as an honest party will not use the dispute process if it is too clostly (and thus they cannot self-enforce the application's correct execution). 
The case study also highlighted that as the application cannot be progressed withing the channel then, for liveness to be preserved, they would have to made on-chain. This could be expensive if the application required computationally complex progressions or if the number of transactions was high.
We propose, \emph{State Assertion Channels}, which has a command-issuance dispute process\footnote{The assertion concept isn't compatible with closure channels as the full state is required to re-deploy an application.}.  and overcomes the issue of sending the application's full state by leveraging the concept of an optimistic contract.
Our contributions:

\begin{itemize}
	\item We propose the first state channel that ensures an honest party never pays the cost to send the application's full state during the dispute process.
	\item This state channel is also the first to make the cost of progressing the application as part of a dispute process independent of the computational complexity of the application, and instead just a function of the number of transactions made in progressing the application.
	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 
\end{itemize}

@@

An optimistic smart contract trades the cost of computation with time.
This lets a smart contract accept an application's new state if no one has proved it is invalid within a fixed challenge period. 
Briefly, one party submits the application's $\stateinfoi$, a command $\cmd$, its $\inputs$, the next $\stateinfoplus$ and a financial bond. 
This asserts that $\stateinfoplus$ is the next state if the smart contract were to compute  $\stateinfoplus = \texttt{Transition}(\stateinfoi, \cmd, \inputs)$. 
Other interested parties can compute the transition locally to verify its validity.
If the asserted state is invalid, then anyone can issue a challenge by notifying the smart contract to compute the transition.
If the challenge is successful, then the bond is used to refund the challenger. 
Eigenmann, Moore and Johnson provided the first demo implementation of an optimistic contract for the Ethereum Name Service
\cite{optimisticcontracts}, but so far this technique has alluded real-world use.

\paragraph{Command Issuance State Channels}
Sprites proposed the concept of a command-issuance state channel, and since then it has been extended by PISA \cite{mccorry2018pisa}, Counterfactual \cite{counterfactual} and Magmo \cite{magmo}. 
At a high level, one party can submit the latest $\stateinfoi$ agreed by all parties before triggering the dispute process.
The smart contract provides a fixed time period for all parties to submit commands and the contract is responsible for computing every command (i.e. state transition).
In Sprites (and PISA), all commands are executed after the dispute process has expired.
Whereas in Counterfactual and Magmo, the command is executed when it is submited and the dispute period's expiry time is reset (i.e. it dispute period is extended for every command). 
The dispute process can be cancelled if one party submits a later state agreed by all parties, or after the expiry time.

\section{State Assertion Channels}
We provide a high level overview of a state assertion channel to show how it combines optimistic contracts and command issuance channels.
Afterwards we'll provide a list of assumptions for the application contract $\appblue$ to ensure new assertions can always be challenged. 
Finally we'll present the state assertion channel contract $\chanblue$ and the interaction amongst both parties, $\chanblue$ and $\appblue$.

@@

The state assertion contract $\chanblue$ and the application contract $\appblue$ must be deployed on the blockchain.
Each party must lock coins into the state channel before they can begin co-operatively executing the application off-chain amongst themselves. 
If there is a disagreement off-chain, then both parties can continue its progression via the dispute process.
Our contribution involves changing the dispute process to avoid sending the full application's state, and to avoid computing the next states on-chain.
Instead parties will assert an application's new state by submitting a hash of the previous state $\hstatei$, the command $\cmd$, its $\inputs$, a hash of the next state $\hstateplus$ and a financial \texttt{bond}. 
%This asserts that $\hstateplus$ represents the application's new state if the command (and its input) was executed by $\appblue$. 
The dispute process provides a fixed time period for the counterparty to verify the assertion by computing the state transition locally. 
To challenge an assertion, the party submits the previous $\stateinfominus$ which lets $\chanblue$ verify the assertion was indeed correct by executing the transition via $\appblue$.  
If the honest party successfully challenges an assertion and proves it is invalid, then they are sent the \texttt{bond} as a refund.
Thus an honest party can always continue an application's execution by asserting a hash of the next state, and they are always refunded the cost of challenging an invalid assertion.

@@

\paragraph{Turn-based application} 
We assume it is a turn-based application and each party performs their state transition in turn until a terminal state is reached.
As well, $\appblue$ must be instantiated on the blockchain to ensure its address is provided to the  state assertion contract $\chanblue$.

@@

\paragraph{Channel status} 
The channel has three flags $\texttt{Status} = \{\DEPOSIT, \ON, \DISPUTE\}$. 
Both parties must deposit coins in $\chanblue$ before it will transition from $\DEPOSIT \rightarrow \ON$.  
While the channel's status is set as $\ON$ both parties can co-operatively continue the application's progression off-chain by exchanging signatures for new states.
If there is a disagreement about a state transition, then one party can trigger a dispute which changes the status from $\ON \rightarrow \DISPUTE$.
%The contract self-enforces a turn-based dispute process.
%One party asserts a new state, and the other party can either challenge it by %notifying the contract to check the state transition, or they can approve it %by asserting a new state which extends it. 
%The dispute process can only finish and let the status change from $\DISPUTE %\rightarrow \ON$ if one party submits a co-operatively signed new state.

@@

\paragraph{Proof of concept implementation} 
We developed a proof of concept for the Ethereum blockchain. Our smart contract is written in Solidity\footnote{https://github.com/ethereum/solidity}, and gas costs were measured using Ganache\footnote{https://github.com/trufflesuite/ganache-cli}. The contract took 2,943,664 gas to deploy, approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127 which is the real world rate in January 2019. The cost to make a state assertion is 59,774+39.5n gas (\$0.02), where \textit{n} corresponds to the number of bytes supplied as $\inputs$ to the assertion.

@@

\paragraph{Enforcing time-based events} 
The assertion channel is responsible for enforcing time-based events with the dispute period $\Delta$.
% and the application doesn't need to consider it 
When the application is co-operatively progressing off-chain, an honest party will wait for a local timeout before triggering a dispute via the blockchain. 
For every new state assertion, the dispute process is reset to ensure each party has a time period of $\Delta$ to take their next move. 
If a party doesn't assert a new state before the deadline, then the honest party will notify the contract via $\chanblue.\timeoutblue()$.
This terminates the application and sends all coins (including the bonds) to the honest party.

@@

\paragraph{Offline parties and PISA} 
%There are two issues for a watching service like PISA \cite{mccorry2018pisa} to protect the channel. 
It is possible for an attacker to trigger a dispute with the latest agreed state hash, and then assert an invalid state hash that benefits the attacker.
Thus, if a party is offline and unable to challenge, an attacker can transition the channel to a state that was never agreed to by the party and does conform to a valid state transition.
If the party uses a watching service, like PISA \cite{mccorry2018pisa}, then the watching service must have a copy of the latest state in plaintext to verify the invalid state transition and challenge, but this hinders state privacy.
%Second, an attacker can issue a new state assertion and claim all coins after the deadline using $\chanblue.\timeoutblue()$. 
%To prevent a timeout, the offline party must delegate the authority to continue the application's execution to the watching service.
%Future work should consider whether the execution of an application can\ be delegated to a third party in an accountable manner.

\paragraph{N-party state assertions}
The state assertion paradigm can be extended to n-party state channels. To do so these channels would require that turns progress in a round-robin fashion, and that $\chanblue$ store the last \textbf{n} state assertions. This is so that a party can be sure that a state assertion will not be accepted unless they explicitly apply their own state assertion after it.

@@

\begin{figure}[H]
	\begin{boxedminipage}{\columnwidth}
		\begin{tabular}{l}
			\contract StateAssertionChannel \{ \\
			\quad $\enum$ Status \{$\DEPOSIT$, $\ON$, $\DISPUTE$\}, $\addr$[] plist; \\
			\quad Status status; $\uintno$ deadline; $\hashblue$ $\hstatei$, $\uintno$ i; $\addr$ turn; \\ %\comment{// Latest state info}  \\
			\quad $\addr$ asserter; $\hashblue$ $\hstateplus$; $\bytes$ input; $\uintno$ cmd; $\bool$ assertion; \\
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ setstate($\bytes[]$ \_sigs, $\uintno$ \_i, $\addr$ \_turn, $\hashblue$ \_$\hstatei$) \{ \\
			\quad \quad \require(\_i $>$ i)); \comment{ // Largest counter so far} \\
			\quad \quad $\hashblue$ hmsg = hash(\_i, \_$\hstatei$,\_turn, $\addr(\this)$);  \\
			\quad \quad \require(verifySigs(hmsg, sigs, plist));  \comment{// Everyone signed new hstate} \\
			\quad \quad delete(input,cmd,\hstateplus,asserter, assertion); \comment{// Delete assertion}\\
			\quad \quad status = Status.\ON; i = \_i; $\hstatei$ = \_$\hstatei$;  turn = \_turn; \comment{// Agreed state} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ triggerDispute() \{ \\
			\quad \quad $\require$(status == Status.ON \& onlyParties()); \comment{// Only parties trigger} \\
			\quad \quad  status = Status.DISPUTE; deadline = now + disputePeriod;\\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ assertState($\hashblue$ \_$\hstatei$, $\hashblue$ \_$\hstateplus$, $\bytes$ \_input, $\uintno$ \_cmd) \{ \\
			\quad \quad $\require$(status == Status.DISPUTE \texttt{AND} checkCallerTurn()); \\
			\quad \quad $\ifs($!assertion)  \{ \\ 
			\quad \quad \quad assertion = true; $\require(\hstatei == \_\hstatei)$ \comment{// First assertion}  \\ 
			\quad \quad \} $\elses$ \{ $\require$($\hstateplus$ == \_$\hstatei$); \} \comment{// Extending existing assertion} \\ 
			\quad \quad asserter = $\msgsender$; input = \_input; cmd = \_cmd; \comment{// Store assertion} \\
			\quad \quad $\hstatei$ = $\hstateplus$; $\hstateplus$ = \_$\hstateplus$; \comment{// i accepted. i+1 assertion} \\ 
			\quad \quad deadline = now + disputePeriod; \comment{// Reset deadline after an assertion} \\
			\quad \quad progressTurn()); \comment{// Increment the turn counter} \\
			\quad \}

		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ challengeAssertion($\bytes$ \_oldstate) \{ \\
			\quad \quad $\require$(status == Status.DISPUTE \texttt{AND} 		checkCallerTurn()); \\
			\quad \quad \require($\hstatei$ == hash(\_oldstate) AND assertion); \comment{// Assertion exists} \\
			\quad \quad $\hashblue$ check = $\appblue.\transitionblue$(asserter, \_oldstate, input, cmd); \comment{// Compute} \\ 
			\quad \quad $\ifs$($\hstateplus$ != checkh) \{ \comment{// Send all coins and bond to non-cheater.}  \} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ timeOut() \{ \\
			\quad \quad \require(now $>=$ deadline \&\& status == Status.dispute); \\ 
			\quad \quad \comment{// Send all coins/bonds to asserter (i.e. last party to respond).} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ resolve($\uintno$ balance1, $\uintno$ balance2) \{ \\
			\quad \quad $\ifs$(status == Status.Dispute) \{ \\
			\quad \quad \quad $\require$(checkCallerTurn()); \comment{// Non-asserter must resolve b4 timeout.} \\
			\quad \quad \} $\elses$ \{ \require(status == Status.ON); \} \comment{// No on-going dispute.} \\ 
			\quad \quad $\require$(hstate == hash(balance1, balance2)); \comment{// Terminal state?} \\
			\quad \quad \comment{// Send each party their final balance and bond.} \\
			\quad \}
		\end{tabular}

	   	\begin{tabular}{l}
	   		\quad $\oninput$ deposit(); \comment{// Not implemented due to space - INCLUDES BOND} \\
	   		\quad $\oninput$ onlyParties() $\returns(\bool)$; \comment{// Check if tx signer is whitelisted} \\
	   		\quad $\oninput$ refundAllBonds() $\internal$; \comment{// Refunds all bonds} \\
	   		\quad $\oninput$ checkCallerTurn() $\returns$($\bool$); \comment{Enforce turn based disputes} \\
	   		\quad $\oninput$ progressTurn() $\returns$($\bool$); \comment{Update the turn counter} \\
	   		\quad $\oninput$ verifySigs($\bytes$ hmsg, $\bytes[]$ sigs, $\addr[]$ signers) $\returns(\bool)$; \\
	   		\}
	   \end{tabular}
	\end{boxedminipage}
